Stream of Consciousness Literature: A 'Joyceless' Linguistic Landscape

### 2024-04-25 paper/paper.qmd
final paper updates

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-sentiment-frequency
#| layout-ncol: 2
#| fig-cap: "Boxplots of Sentiment Scores by Author (Bing & NRC)"
#| fig-subcap: ["Bing lexicon", "NRC lexicon"]

>>>>

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-sentiment-frequency
#| layout-ncol: 2
#| fig-cap: "Boxplots of Sentiment Scores by Word Frequency (Bing & NRC)"
#| fig-subcap: ["Bing lexicon", "NRC lexicon"]
